### 2020-02-25 paper/results.tex
Addressing Osama's comments

More changes in thermal neutron flux shape and magnitude during the reactor 
operation for the $^{233}$U case are observed in the inner core zone 
($R\lesssim150$) than in the outer core zone. In the outer core zone, 
significant changes during reactor operation are observed for the thermal 
neutron flux for the reactor-grade Pu case. In contrast, for the TRU case, 
thermal neutron flux change in the outer core zone is almost negligible. 
Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively significant changes in thermal flux leakage from the core for the 
Pu (equilibrium composition) and TRU (initial and equilibrium composition) 
cases. The SD-TMSR core design was optimized for $^{233}$U  
\cite{li_optimization_2018}; thus, the core geometry (e.g., channel lattice 
pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.

>>>>

More changes in thermal neutron flux shape and magnitude during the reactor 
operation for the $^{233}$U case are observed in the inner core zone 
($R\lesssim150$) than in the outer core zone. In the outer core zone, 
significant changes during reactor operation are observed for the thermal 
neutron flux for the reactor-grade Pu case. In contrast, for the TRU case, 
thermal neutron flux change in the outer core zone is almost negligible. 
Additionally, Figure~\ref{fig:thermal_flux} shows 
relatively significant changes in thermal flux leakage from the core for the 
Pu (equilibrium composition) and TRU (initial and equilibrium composition) 
cases. The SD-TMSR core design was optimized for $^{233}$U  
\cite{li_optimization_2018}; thus, the core geometry (e.g., the channel lattice 
pitch) must be re-optimized for another type of fuel to obtain better 
neutronics performance.
